---
title: "figures"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{figures}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(changepointsR)
library(ggplot2)
```

The code below is for Figure 2(a), except that the number of simulations is set to 100 rather than 1000, to speed up the run time. We simulate under $H_0$, apply binary segmentation, and implement our post-selection inference method for different values of $N$. All $\boldsymbol{\psi}$'s are chosen randomly.

To reproduce the exact figure from the paper, change num_iter to 1000. To get Figure 2(b), set h = 20.

```{r plots}
set.seed(100)

h <- 10
n <- 1000 ## size of dataset
num_iter <- 100 ## number of simulations

pvals <- matrix(NA, nrow=num_iter, ncol=5)

iter <- 1
while( iter <= num_iter ){
  y <- rnorm(n)
  results <- binary_segmentation(y, threshold=3.5)
  if ( length(results$changepoints) >= 1 ){ ## only keep simulations for which the changepoint algorithm detects at least one changepoint
    if ( results$changepoints[1] >= h & results$changepoints[1] <= (n-h) ){
      x <- calculate_pvals(y, results, N=50, h=h, sigma2=1, num_pvals=1)
      pvals[iter,1] <- x$P_both[1] / x$P_phi_in_S[1]
      pvals[iter,2] <- sum(x$P_both[1:5]) / sum(x$P_phi_in_S[1:5])
      pvals[iter,3] <- sum(x$P_both[1:10]) / sum(x$P_phi_in_S[1:10])
      pvals[iter,4] <- sum(x$P_both[1:20]) / sum(x$P_phi_in_S[1:20])
      pvals[iter,5] <- sum(x$P_both[1:50]) / sum(x$P_phi_in_S[1:50])
      iter <- iter + 1
    }
  }
}
pvals[pvals>1] <- 1 ## some p-values are slightly above 1 because of floating point errors
pvals <- pvals[rowSums(is.na(pvals))==0,]
colnames(pvals) <- paste0("N", c(1, 5, 10, 20, 50))

## Sort p-values
pvals_sorted <- matrix(NA, nrow=nrow(pvals), ncol=ncol(pvals))
for ( i in 1:5 ){
  pvals_sorted[,i] <- sort(pvals[,i])
}

## Plot p-values against theoretical quantities from U(0,1)
dat <- data.frame(x=rep(seq(0, 1, length.out=nrow(pvals_sorted)), 4), y=as.vector(pvals_sorted[,c(1,2,3,5)]), 
                  N=rep(as.factor(c(1, 5, 10, 50)), each=nrow(pvals_sorted)))
ggplot(dat) + geom_point(aes(x=x, y=y, colour=N)) + geom_line(aes(x=x, y=y, colour=N)) +
  geom_abline(intercept=0, slope=1) + labs(x="p-value", y="")
```

Figure 2(c). As above, to reproduce the plot in the paper set num_iter = 1000. To reproduce Figure 2(d) also set h = 20.

```{r plots}
set.seed(100)
h <- 10
n <- 1000
num_iter <- 100
pvals <- matrix(NA, nrow=num_iter, ncol=5)
iter <- 1
while( iter <= num_iter ){
  y <- rnorm(n)
  results <- binary_segmentation(y, threshold=3.5)
  if ( length(results$changepoints) >= 1 ){
    if ( results$changepoints[1] >= h & results$changepoints[1] <= (n-h) ){
      x <- calculate_pvals(y, results, N=50, h=h, sigma2=1, num_pvals=1, include_original=TRUE)
      pvals[iter,1] <- x$P_both[50] / x$P_phi_in_S[50]
      pvals[iter,2] <- sum(x$P_both[c(1:4,50)]) / sum(x$P_phi_in_S[c(1:4,50)])
      pvals[iter,3] <- sum(x$P_both[c(1:9,50)]) / sum(x$P_phi_in_S[c(1:9,50)])
      pvals[iter,4] <- sum(x$P_both[c(1:19,50)]) / sum(x$P_phi_in_S[c(1:19,50)])
      pvals[iter,5] <- sum(x$P_both) / sum(x$P_phi_in_S)
      iter <- iter + 1
    }
  }
}
pvals[pvals>1] <- 1 ## some p-values are slightly above 1 because of floating point errors
pvals <- pvals[rowSums(is.na(pvals))==0,]
colnames(pvals) <- paste0("N", c(1, 5, 10, 20, 50))

## Sort p-values
pvals_sorted <- matrix(NA, nrow=num_iter, ncol=5)
for ( i in 1:5 ){
  pvals_sorted[,i] <- sort(pvals[,i])
}

## Plot p-values against theoretical quantities from U(0,1)
dat <- data.frame(x=rep(seq(0, 1, length.out=num_iter), 4), y=as.vector(pvals_sorted[,c(1,2,3,5)]), 
                  N=rep(as.factor(c(1, 5, 10, 50)), each=num_iter))
ggplot(dat) + geom_point(aes(x=x, y=y, colour=N)) + geom_line(aes(x=x, y=y, colour=N)) +
  geom_abline(intercept=0, slope=1) + labs(x="p-value", y="")
```

Figure 3.

(re-run with new threshold set!)

```{r echo=FALSE, warning=FALSE}
n <- 1000
h <- 10
delta <- 1
num_iter <- 100

pvals <- matrix(NA, nrow=num_iter, ncol=6)
iter <- 1
while( iter <= num_iter ){
  y <- rnorm(n) + c(rep(delta/2,n/2), rep(-delta/2,n/2))
  results <- binary_segmentation(y, threshold=3.5)
  if ( length(results$changepoints) >=1 ){
    if ( results$changepoints[1] >= h & results$changepoints[1] <= (n-h) ){
      x <- calculate_pvals(y, results, N=50, h=h, include_original=TRUE, num_pvals=1)
      pvals[iter,1] <- x$P_both[50] / x$P_phi_in_S[50]
      pvals[iter,2] <- sum(x$P_both[c(1,50)]) / sum(x$P_phi_in_S[c(1,50)])
      pvals[iter,3] <- sum(x$P_both[c(1:4,50)]) / sum(x$P_phi_in_S[c(1:4,50)])
      pvals[iter,4] <- sum(x$P_both[c(1:9,50)]) / sum(x$P_phi_in_S[c(1:9,50)])
      pvals[iter,5] <- sum(x$P_both[c(1:19,50)]) / sum(x$P_phi_in_S[c(1:19,50)])
      pvals[iter,6] <- sum(x$P_both) / sum(x$P_phi_in_S)
      iter <- iter + 1
    }
  }
}
pvals[pvals>1] <- 1 ## some p-values are slightly above 1 because of floating point errors
colnames(pvals) <- paste0("N", c(1, 2, 5, 10, 20, 50))


### Figure 3(a): QQ plot vs. H0
pvals_sorted <- matrix(NA, nrow=num_iter, ncol=6)
for ( i in 1:6 ){
  pvals_sorted[,i] <- sort(pvals[,i])
}
dat <- data.frame(x=rep(seq(0, 1, length.out=num_iter), 6), y=as.vector(pvals_sorted), 
                  N=rep(as.factor(c(1, 2, 5, 10, 20, 50)), each=num_iter))
ggplot(dat) + geom_point(aes(x=x, y=y, colour=N)) + geom_line(aes(x=x, y=y, colour=N)) +
  geom_abline(intercept=0, slope=1) + labs(x="p-value", y="")

### Figure 3(b): QQ plot vs. p-values from Jewell & al.
dat <- data.frame(x=rep(pvals_sorted[,1], 5), y=as.vector(pvals_sorted[,2:6]), 
                  N=rep(as.factor(c(2, 5, 10, 20, 50)), each=num_iter))
ggplot(dat) + geom_point(aes(x=x, y=y, colour=N)) + geom_line(aes(x=x, y=y, colour=N)) +
  geom_abline(intercept=0, slope=1) + labs(x="p-value", y="")
  
```


Figure 4: Power plots.
